A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-11-25 01_Introduction.Rmd
more about research history

The spread of ideas in human populations over space and time is a major topic of *Cultural Evolution* research [@creanzaCulturalEvolutionaryTheory2017]. This theoretical framework is as old as theories of biological evolution and underwent a long and versatile research history from *Evolutionism* and *Social Darwinism* in the 19th and early 20th century, against *Cultural relativism* to *Neoevolutionism* up until the ninteen sixties and seventies [@petermannGeschichteEthnologie2004].

>>>>

The spread of ideas in human populations over space and time is a major topic of *Cultural Evolution* research [@creanzaCulturalEvolutionaryTheory2017]. This theoretical framework is as old as theories of biological evolution and underwent a long and versatile research history from *Evolutionism* and *Social Darwinism* in the 19th and early 20th century, against *Cultural relativism* to *Neoevolutionism* up until the ninteen sixties and seventies [@petermannGeschichteEthnologie2004]. In the seventies the the discussion took another turn away from social structure to the more general observation of human behaviour. Three major theoretical movements emerged in this context: *Evolutionary Psychology*, *Human Behavioural Ecology* and *Dual Inheritance Theory* [@smithThreeStylesEvolutionary2000]. The latter -- heavily popularized by Richard Dawkin's *Memetics* [@dawkinsSelfishGene1976] -- establishes ...
